---
title: "DataSci 306 Final Project Preprocessing File"
author: "Aioyla Zhang, Alok Swaminathan, Duncan Chen"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

-   Create a new file in the `data/` directory called "Preprocessing.Rmd". The remaining instructions in this section are to be completed in that file.
-   Write a function that will load a table from the IMDb files in the `data/` directory.
    -   The function should take the file name (without the ".csv.gz" portion) as an argument
    -   The function should load the appropriate `.csv.gz` file.
    -   Make sure that all "\\N" values (which IMDB uses to indicate missing values) are turned into proper NA values in R
    -   The function should return the table.
-   For each of the `.csv.gz` files, use your function to load the table, then save it into a variable (e.g. `name_basics <- preprocess("name_basics")`) and use the `write_rds` function (e.g., `write_rds(name_basics, "name_basics.rda")`.
-   Run the function on all of the `*_sample.csv.gz` files to created processed `.rda` files.

```{r}
load_csv <- function(name) {
  name <- paste0(name,".csv.gz")
  read.csv(
    name,
    na.strings = "\\N"
  )
}
```

```{r}
files <- c("name_basics_sample","title_basics_sample",
           "title_principals_sample","title_ratings_sample")
for (file in files) {
  load_csv(file) |>
    write_rds(
      paste0(file,".rda")
    )
}
```


